%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Edward Hu} % Your name
\address{2819 Deeds Road \\ Houston, TX 78705} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{https://github.com/BDHU}
\address{(512)~$\cdot$~999~$\cdot$~0319 \\ bodunhu@utexas.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Texas at Austin} \hfill {\em December 2016 - May 2020} \\ 
B.S. in Computer Science \& Mathematics \\
%Minor in Linguistics \smallskip \\
GPA: 3.72

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{University of Texas at Austin}{August 2016 - Present}{Student Researcher}{Austin, TX}
\item Used OpenCV to detect the defects generated during 3D printing and halt the process if necessary.
\item Construct artificially neural networks with multiple layers.
\item Use gradient descent and genetic algorithms to optimze the performance of the ANN.
\item Utilized numpy and matlibplot for the optimization and graphing tasks.
\item Use Python to modify the Gcode file used to guide the 3D printing process.
\item Use optimization methods to find the optimal solution to cut 3D printed object to reduce support structure required.

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{Technical Experiences}
\begin{rSubsection}{Projects}{}{}{}
\item \textit{Minesweeper Optimization}: Used NEAT framework to implement ANN to improve the efficiency of minesweepers.
\item \textit{Character Recognizer}: Implement a two-layer neural network to improve its accuracy on predicting the hand-written digits.
\item \textit{File Compressor}: Used huffman coding method to compress a file, reduce the size of the file, and restore the compressed data.
\item \textit{Browser}: A browser for macOS that has basic function to browse webpages.
\end{rSubsection}

\begin{rSubsection}{Extra curriculum}{}{}{}
\item Robotics Club: Compete in Region 5
\end{rSubsection}

\begin{rSubsection}{Curriculum}{}{}{}
\item Data Structure, Intro to Computer Architecture, Intro to Computer Systems, Computational Intelligence in game AI.
\end{rSubsection}

\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Java, C/C++, Python, Swift, \LaTeX, Matlab \\
Tools & Linux, Git, Vim, GCC, Docker, Intellij, Xcode \\
Languages & Chinese, English
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
